A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-07 manuscript.Rmd
more verbose explanations of what is happening here....

The `repro` package is particularly well-suited for computationally intensive data analyses and simulations that  are to be run on distributed computing environments. By using containers, `repro` ensures identical execution across platforms and thus guarantees that a data analysis or simulation that was designed and tested on a local computer will be executed in the identical manner on a remote machine or various remote machines across an entire computing cluster. Thereby, the repro package makes massive parallel computing in heterogeneous computing environments less error-prone while ensuring the full documentation of all computational steps taken — even if some or all of them were run in parallel on distributed platforms.
Alone the sheer data size often warrants distributed computing, e.g. the European Bioinformatics Institute stores more than 120 Petabyte of publicly accessible data [@cookEuropeanBioinformaticsInstitute2018], single FMRI studies quickly amount to hundreds of Gigabyte[^openneuro] and even purely behavioral data like from the moral machine experiment [>10GB, @awadMoralMachineExperiment2018] can become to big to handle .

[^openneuro]: https://openneuro.org/public/datasets

As default, `repro` uses Docker, which is the defacto standard for cloud computing, as a container solution.
However, Docker requires administrator rights for execution. Whereas this is no issue on most modern cloud computing infrastructures, it is often an issue in classic HPC environments.
Singularity <!--AP add reference --> is an alternative solution. It was designed to run without administratot rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Importantly, this choice does not affect how code is executed inside the container.
Like with Docker, the default `Makefile` generated by `repro` comes with a mechanism to automatically send all commands to Singularity. To reproduce an analysis with Singularity, simple add the parameter `SINGULARITY=TRUE` as follows:

>>>>

The `repro` package is particularly well-suited for computationally intensive data analyses and simulations that  are to be run on distributed computing environments. By using containers, `repro` ensures identical execution across platforms and thus guarantees that a data analysis or simulation that was designed and tested on a local computer will be executed in the identical manner on a remote machine or various remote machines across an entire computing cluster. Thereby, the repro package makes massive parallel computing in heterogeneous computing environments less error-prone while ensuring the full documentation of all computational steps taken — even if some or all of them were run in parallel on distributed platforms. <!-- AP can we add examples, are there open repositores eg from neuroscience that have massive datasets published or massive simulations? -->
As default, `repro` uses Docker, which is the defacto standard for cloud computing, as container solution.
However, Docker requires administrator rights for execution. Whereas this is no issue on most modern cloud computing infrastructures, it is often an issue in classic HPC environments.
Singularity <!--AP add reference --> is an alternative solution. It was designed to run without administratot rights, while maintaining full compatibility with Docker images.
If you already have a Docker image, you can choose if you want to run this image with Docker or with Singularity.
Importantly, this choice does not affect how code is executed inside the container.
Like with Docker, the default `Makefile` generated by `repro` comes with a mechanism to automatically send all commands to Singularity. To reproduce an analysis with Singularity, simple add the parameter `SINGULARITY=TRUE` as follows:
